
```{css, echo=FALSE,eval=T}
/*table {
  width: 100% !important;
  
}*/
pre {
border: 1px solid black;
border-radius: 0.25rem;
background-color: rgba(0, 0, 0, 0.04);

}

```

```{r}
#dataset<-7
```

```{r,src,echo=F,warning=F,message=F,results='hide',fig.keep='none'}
#eval.n<-7
library(knitr)
 run<-15302
# dataset<-11
#run<-15303
dataset<-11

reload<-F
target<-c("obs","ref")
ref_target<-"obs"
rel<-T
det<-c(T,F)
conditions<-letters[1:6]
limit<-T
author<-T
ifelse(limit,ceiling<-"outliers removed","outliers not removed")
# if(reload)
#   rm(eval.1)
source(paste0(Sys.getenv("GIT_TOP"),"/SPUND-LX/psych/HA/eval-init-vars.R"),echo = F)
source(paste0(Sys.getenv("GIT_TOP"),"/SPUND-LX/psych/HA/eval-003.R"),echo = F)
if(reload)
  eval.1<-get.anovas(dfa,target,conditions,det,rel,ref_target,author)
anova.form<-eval.1$anova.form
lme.form<-eval.1$lme.form
caption.ext<-ifelse(rel,paste0(", normalised to ",ref_target,", distance ceiling =  ",ceiling),paste0("not normalised, distance ceiling =",ceiling))
dfe<-eval.1$plot.md

```

# appendix
eval output M`r dataset``r caption.ext`.

# testcite
## method (M`r dataset`)
To compute distances we queried a corpus for matching conditions where certain (assumed) determiners appear before similar nouns. In M`r dataset` (removed...)  This distance should give us information structural evidence of how strong these noun occurences are connected, i.e. if a noun appears out of the blue mostly or if it somewhere before has been introduced to the audience. In information structure definitions this would be termed with **given and new information** [@prince_toward_1981].


## legende
```{r,legend,echo=FALSE,warning=F,message=F}
legend<-data.frame(variable=c("target","q","det",paste0("q:",letters[1:6])),
                   explanation=c("corpus","condition","antecedent POS==DET",rep("query condition",6)),
                   values=c("obs,ref","a,b,c,d,e,f","TRUE,FALSE",
                            ".*","this,that,those,these","the","a,an,any,some","my","his,her,their,your")
                   )
#library(kableExtra)

# k<-kable(legend,caption = "model vars")
# k<-kable_styling(k,full_width = TRUE)
# k
 kable(legend, caption = "model vars",format="markdown")
#kable(legend, caption = "model vars")

```

## anova analysis
### anova plain, formula: [``` `r anova.form` ```]
```{r,dfs1,echo=FALSE,warning=F,message=F}
# legend<-data.frame(variable=c("target","q","det",paste0("q:",letters[1:6])),
#                    explanation=c("corpus","condition","antecedent POS==DET",rep("query condition",6)),
#                    values=c("obs,ref","a,b,c,d,e,f","TRUE,FALSE",
#                             ".*","this,that,those,these","the","a,an,any,some","my","his,her,their,your")
#                    )
# #library(kableExtra)
# 
# # k<-kable(legend,caption = "model vars")
# # k<-kable_styling(k,full_width = TRUE)
# # k
# kable(legend, caption = "model vars") #%>%
# #  kable_styling(full_width = TRUE)
s1<-eval.1$anova.plain
p.select<-c("target|target:q")
p.an<-s1[grep(p.select,rownames(s1)),]
#p.an
#cat("anova plain, formula: `",anova.form.l$pre.det,"`\n")
s1
```

### anova of linear regression model: [`anova(summary(lmer))`]

```{r,dfs2,echo=FALSE,warning=F,message=F}



s2<-eval.1$anova.lme
p.an.lm<-s2[grep(p.select,rownames(s2)),]
#p.an.lm
#cat("anova of linear regression model (below): [`anova(summary(lmer))`]\n")
s2
```

### linear regression coefficients, formula: [``` `r lme.form` ```]
```{r,dfs3,echo=FALSE,warning=F,message=F}
s3<-eval.1$lme
#cat("linear regression coefficients, formula: `",lmeform.l$pre.det,"`\n")
#print(s3, right = TRUE, width = 999)
#print(s3)
#options(max.print = 1000)  # Set higher limit
invisible(capture.output(
  suppressWarnings(
    suppressMessages(
      print(s3)
    )
  ), type = "message"
))
#print(s3)
coef<-s3$coefficients
### relations:
int<-coef[1,1]
#int
qv<-coef[9:(length(coef[,1])),1]
qvc<-qv
#qvc

qvc.ns<-strsplit(names(qvc),"q")
qvc.ns<-lapply(qvc.ns, function(x){
  return(x[2])
})
qvc.ns<-unlist(qvc.ns)
names(qvc)<-qvc.ns
#l<-length(qvc.ns[[1]])
qdiff<-int+qv
qmin<-qdiff<int
qvmin<-qv[qmin]
names(qvmin)<-names(qvc)[qmin]
#qvmin
```

## plots
```{r boxplot1,echo=F,warning=F,message=F, fig.cap=paste0("compare distances by corpus",caption.ext)}
# df1_no_outliers <- dfa %>%
#   group_by(target) %>%
#   filter(
#     dist >= quantile(dist, 0.25) - 1.5 * IQR(dist),
#     dist <= quantile(dist, 0.75) + 1.5 * IQR(dist)
#   ) %>%
#   ungroup()
d.sel<-paste0("dist_rel_",ref_target)
Y<-dfa[[d.sel]]
boxplot(Y~target,dfa,outline=F,notch=T,varwidth=T,ylab = d.sel)

```

```{r,barplot-median,echo=F,warning=F,message=F,fig.cap=paste0("mean distances over query/corpus",caption.ext),eval=TRUE}
m1<-which(colnames(dfe)%in%c("mean","median"))
dfe[,m1]<-round(dfe[,m1],0)
# m2<-m1[length(m1):1]
# m3<-c(1:(m1[1]-1),m2)
# dfe<-dfe[,m3]
plot.dist(dfe,"mean")
```


```{r,dfe-table,echo=F,warning=F,message=F}
kable(dfe,caption = paste0("mean/median table for M",dataset),format="markdown")
```


```{r,barplot-mean,echo=F,warning=F,message=F,fig.cap=paste0("median distances over query/corpus",caption.ext),eval=TRUE}
plot.dist(dfe,"median")

```

```{r lmeplot,echo=F,warning=F,message=F,fig.cap=paste0("distances relation",caption.ext)}
rmd.plot.lme(s3)
```

```{r gplot,echo=F,warning=F,message=F,fig.cap="distances normalised vs. raw"}
gplot.dist(dfa,ref_target)
```
-----

## REF {#REF-1}

<!--## refs-top {-}
::: {#refs-top}
:::-->

